Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-11-19 papers/integration/omm_integ.tex
A few more lines...

% Change this - we already talked about channels in the context of the
% three channel model show. Perhaps modify to talk about how we have a
% map of channels - almost a continuous space in the \ccg model. This
% can then lead on to Fig 3.
\rvwt{Expand along lines of `the
action space for reflexive saccade end points is therefore
continuous rather than discrete' (FIXME).}

>>>>

% Change this - we already talked about channels in the context of the
% three channel model show. Perhaps modify to talk about how we have a
% map of channels - almost a continuous space in the \ccg model. This
% can then lead on to Fig 3.
\rvwt{The GPR model in Fig.~\ref{ccg_model}(b) has only three
channels with focussed inhibition from striatum to SNr and GPe defined
by a simple one-to-one scheme. The action channels represent discrete,
incompatible motor action choices. In the oculomotor model, an action
channel might represent the end-point of saccade, and the competition
carried out in the basal ganglia is between potential saccade
end-points. However, eye movements have a \e{continuous} end-point
space; the eye can rotate to any orientation within its
biomechanically permissible range. Some end-points within this range
are certainly mutually exclusive---it's not possible to look to the
left and to the right simultaneously---but \e{nearby} end-points are
not necessarily incompatible. A small enough error in the end-point of
a saccade will not prevent the eye from foveating on a target as the
fovea is not infinitesimally small. To cope with this requirement,
the populations within the oculomotor basal ganglia are conceived of
as two-dimensional topographic grids of neural elements. Activity in
each element corresponds to a spatial location in the visual
field. \cite{someref} here.}
